Abstractions for Multi-Sorted Substitutions

### 2023-08-29 paper/paper.tex
Update.

  \subsection{A Structure for Multi-Sorted Syntax}
  The multi-sorted syntax makes it easy to capture general syntax definitions
  in a structure:
  \LibCode\KTerms
  The first three fields record the definitions of sorts, terms, and variable introduction.
  The last field records that variable introduction
  \ACode{\AField{`\_}} is injective, which is trivially true for
  constructors. The instantiation for our System F syntax is
  straightforward:
  \AppCode\FTerms

>>>>

  \subsection{A Structure for Multi-Sorted Syntax}
  The multi-sorted syntax makes it easy to define a structure for
  syntaxes of arbitrary object-languages, i.e.\ syntaxes with
  arbitrary amounts of syntactic categories and variables:
  \LibCode\KTerms
  The first three fields record the definitions of sorts, terms, and variable introduction.
  The last field records that variable introduction
  \ACode{\AField{`\_}} is injective, which is trivially true for
  constructors. The instantiation for our System F syntax is
  straightforward:
  \AppCode\FTerms
